### 2017-12-12 readme.rmd
typo

*Figure 4 - Detailed examination of the analysis subset (indicated in upper right pane) that is the focus of the conclusions by Feuda et al. These are the six recoded CAT-GTR+G analyses with posterior predictive (PP) scores. The presented statistics for these six cells are posterior probability of Poifera-sister, Maxdiff (with lower scores indicating better convergence), and five PP scores (where lower absolute value indicates better model adequacy). Only one analysis provides significant support for Porifera-sister. It isn't the most adequate by any of the PP scores, and showed the poorest convergence according to Maxdiff. Recodings are: None- K - KGB-6, D - Dayhoff-6, and S- SR-6.*

@@

The other statistics help put this single significant result into context, and they could be used to provide explicit criteria for favoring the one significant result over the five insignificant results. Feuda *et al.* present PP as the primary criterion we should consider. The one analysis with significant support for Porifera-sister does not have the best (lowest absolute value) PP score for any of the five PP statistics considered (Figure 4). By their own criterion of model adequacy, we should favor the unresolved analyses.

>>>>

*Figure 4 - Detailed examination of the analysis subset (indicated in upper right pane) that is the focus of the conclusions by Feuda et al. These are the six recoded CAT-GTR+G analyses with posterior predictive (PP) scores. The presented statistics for these six cells are posterior probability of Porifera-sister, Maxdiff (with lower scores indicating better convergence), and five PP scores (where lower absolute value indicates better model adequacy). Only one analysis provides significant support for Porifera-sister. It isn't the most adequate by any of the PP scores, and showed the poorest convergence according to Maxdiff. Recodings are: None- K - KGB-6, D - Dayhoff-6, and S- SR-6.*

@@

The other statistics help put this single significant result into context, and they could be used to provide explicit criteria for favoring the one significant result over the five insignificant results. Feuda *et al.* present PP as the primary criterion we should consider. The one analysis with significant support for Porifera-sister does not have the best (lowest absolute value) PP score for any of the five PP statistics considered (Figure 4). By their own criterion of model adequacy, we should favor the unresolved analyses. Within these recoded CAT-GTR+G analyses, there is not a trend toward increased support for Porifera-sister with increasing model adequacy.
